SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''

### 2018-09-07 reports/esi2.tex
made b&w and esi finished

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[super,sort&compress,comma]{natbib}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[detect-all]{siunitx}
\usepackage{xr}
\externaldocument{apssamp}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\Roman{table}}
\author{Andrew R. McCluskey,\textit{$^{ab}$}$^{\ddag}$ Adrian Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
Karen J. Edler,\textit{$^{a}$}$^{\ast}$ Stephen C. Parker,\textit{$^{a}$} Andrew J. Jackson,\textit{$^{cd}$} \\
Richard A. Campbell,\textit{$^{ef}$} and Thomas Arnold\textit{$^{abcg}$}$^{\ast}$ \\
 \\
\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton} \\
\textit{Down, Bath, BA2 7AY, UK.} \\
\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE,} \\
\textit{UK.} \\
\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.} \\
\textit{$^{d}$~Department of Physical Chemistry, Lund University,} \\
\textit{SE-211 00 Lund, Sweden.} \\
\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000,} \\
\textit{Grenoble, France.} \\
\textit{$^{f}$~Division of Pharmacy and Optometry, University of} \\
\textit{Manchester, Manchester, M13 9PT, UK.} \\
\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology} \\
\textit{Facilities Council, Rutherford Appleton Laboratory, Harwell} \\
\textit{Oxford, Didcot OX11 0QX, UK.} \\
\textit{$^{\P}$~Present address: Department of Food Technology, Lund} \\
\textit{University, SE-211 00 Lund, Sweden}}
\title{ESI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
\date{}
\begin{document}

@@

\section{Literature values for head and tail volumes}
\begin{table}
	\caption{\ Lipid component volumes extracted from different literature sources. $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
  \centering
	\label{tab:water}
	\begin{tabular}{llllllllll}
		\hline
    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
    \hline
    Reference & [\cite{Armen1998}] & [\cite{Sun1994}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Pan2012}] & [\cite{Kucerka2012}] \\
    \hline
    $V_l$/\si{\angstrom^3} & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1$ & $1155.4\pm30.0$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
    $V_t$/\si{\angstrom^3} & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0$ & $815.9\pm15.5$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
    $V_h$/\si{\angstrom^3} & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
    T/\si{\celsius} & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
	\end{tabular}
\end{table}

@@

%
\begin{table}[h]
	\small
	\caption{\ The invariant parameters within the chemically-consistent model.
	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
	\label{tab:invariant}
  \centering
	\begin{tabular}{ccccc}
		\hline
		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
		\hline
		X-ray & & & & \\
		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
		Air & -- & -- & -- & 0\\
		DES & -- & -- & -- & 10.8$^b$ \\
		\hline
		Neutron & & & & \\
		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
		h-DES & -- & -- & -- & 0.43$^b$  \\
		hd-DES & -- & -- & -- & 3.15$^b$ \\
		\hline
	\end{tabular}
\end{table}
%

@@

@@

	\includegraphics[width=0.50\textwidth]{figures/dmpc5_all_corner}

@@

@@

	\includegraphics[width=0.50\textwidth]{figures/dppc5_all_corner}

@@

@@

	\includegraphics[width=0.50\textwidth]{figures/dmpg5_all_corner}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[super,sort&compress,comma]{natbib}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[detect-all]{siunitx}
\usepackage{xr}
\externaldocument{apssamp}
\usepackage{rotating}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\Roman{table}}
\author{A.~R.~McCluskey,\textit{$^{ab}$}$^{\ddag}$ A.~Sanchez-Fernandez,\textit{$^{ac}$}$^{\ddag\P}$ \\
K.~J.~Edler,\textit{$^{a}$}$^{\ast}$ S.~C.~Parker,\textit{$^{a}$} A.~J.~Jackson,\textit{$^{cd}$} \\
R.~A.~Campbell,\textit{$^{ef}$} and T.~Arnold\textit{$^{abcg}$}$^{\ast}$ \\
 \\
\textit{$^{a}$~Department of Chemistry, University of Bath, Claverton} \\
\textit{Down, Bath, BA2 7AY, UK.} \\
\textit{$^{b}$~Diamond Light Source, Harwell Campus, Didcot, OX11 0DE,} \\
\textit{UK.} \\
\textit{$^{c}$~European Spallation Source, SE-211 00 Lund, Sweden.} \\
\textit{$^{d}$~Department of Physical Chemistry, Lund University,} \\
\textit{SE-211 00 Lund, Sweden.} \\
\textit{$^{e}$~Institut Laue-Langevin, 71 avenue des Martyrs, 38000,} \\
\textit{Grenoble, France.} \\
\textit{$^{f}$~Division of Pharmacy and Optometry, University of} \\
\textit{Manchester, Manchester, M13 9PT, UK.} \\
\textit{$^{g}$~ISIS Neutron and Muon Source, Science and Technology} \\
\textit{Facilities Council, Rutherford Appleton Laboratory, Harwell} \\
\textit{Oxford, Didcot OX11 0QX, UK.} \\
\textit{$^{\P}$~Present address: Department of Food Technology, Lund} \\
\textit{University, SE-211 00 Lund, Sweden}}
\title{SI for ``Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers''}
\date{}
\begin{document}

@@

\section{Literature values for head and tail volumes}
Table \ref{tab:water} gives a variety of literature values for the component volumes of the lipids investigated in this work.
\begin{sidewaystable}
  \centering
	\caption{\ Lipid component volumes extracted from different literature sources. $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
  \centering
	\label{tab:water}
	\begin{tabular}{l|lll|ll|ll|l|l}
    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
    \hline
    Reference & [\cite{Armen1998}] & [\cite{Sun1994}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Armen1998}] & [\cite{Kucerka2004,Balgavy2001}]$^a$ & [\cite{Pan2012}] & [\cite{Kucerka2012}] \\
    \hline
    $V_l$/\si{\angstrom^3} & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1$ & $1155.4\pm30.0$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
    $V_t$/\si{\angstrom^3} & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0$ & $815.9\pm15.5$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
    $V_h$/\si{\angstrom^3} & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
    T/\si{\celsius} & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
	\end{tabular}
\end{sidewaystable}

@@

%
\begin{table}[h]
  \centering
	\caption{\ The invariant parameters within the chemically-consistent model.
	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
	\label{tab:invariant}
	\begin{tabular}{c|c|c|c|c}
		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
		\hline
		X-ray & & & & \\
		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
		Air & -- & -- & -- & 0\\
		DES & -- & -- & -- & 10.8$^b$ \\
		\hline
		Neutron & & & & \\
		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
		h-DES & -- & -- & -- & 0.43$^b$  \\
		hd-DES & -- & -- & -- & 3.15$^b$ \\
	\end{tabular}
\end{table}
%

\section{XRR parameters at each surface pressure}
Tables \ref{tab:liptab1}-\ref{tab:liptab3} gives the best fit values for the custom model that was fitted to each surface pressure, for each lipid. These values were used for comparison to assess the effect of the choline chloride:glycerol on the lipid.
%
\begin{table}
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the second highest surface pressure (SP) measured. The values of $d_t$ were found from the values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn. \ref{equ:phih}}
	\label{tab:liptab1}
	\begin{tabular}{l|l|l|l|l}
		Lipid & DLPC & DMPC & DPPC & DMPG \\
    SP/mNm$^{-1}$ & 30 & 30 & 25 & 25 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle30.txt} & \input{../output/dmpc/angle30.txt} & \input{../output/dppc/angle25.txt} & \input{../output/dmpg/angle25.txt} \\
		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough30.txt} & \input{../output/dmpc/rough30.txt} & \input{../output/dppc/rough25.txt} & \input{../output/dmpg/rough25.txt} \\
    \hline
    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh30.txt} & \input{../output/dmpc/solh30.txt} & \input{../output/dppc/solh25.txt} & \input{../output/dmpg/solh25.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail30.txt} & \input{../output/dmpc/tail30.txt} & \input{../output/dppc/tail25.txt} & \input{../output/dmpg/tail25.txt} \\
	\end{tabular}
\end{table}
%
%
\begin{table}
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the second lowest surface pressure (SP) measured. The values of $d_t$ were found from the values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn. \ref{equ:phih}}
	\label{tab:liptab2}
	\begin{tabular}{l|l|l|l|l}
		Lipid & DLPC & DMPC & DPPC & DMPG \\
    SP/mNm$^{-1}$ & 25 & 25 & 20 & 20 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle25.txt} & \input{../output/dmpc/angle25.txt} & \input{../output/dppc/angle20.txt} & \input{../output/dmpg/angle20.txt} \\
		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough25.txt} & \input{../output/dmpc/rough25.txt} & \input{../output/dppc/rough20.txt} & \input{../output/dmpg/rough20.txt} \\
    \hline
    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh25.txt} & \input{../output/dmpc/solh25.txt} & \input{../output/dppc/solh20.txt} & \input{../output/dmpg/solh20.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail25.txt} & \input{../output/dmpc/tail25.txt} & \input{../output/dppc/tail20.txt} & \input{../output/dmpg/tail20.txt} \\
	\end{tabular}
\end{table}
%
%
\begin{table}
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the lowest surface pressure (SP) measured. The values of $d_t$ were found from the values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn. \ref{equ:phih}}
	\label{tab:liptab3}
	\begin{tabular}{l|l|l|l|l}
		Lipid & DLPC & DMPC & DPPC & DMPG \\
    SP/mNm$^{-1}$ & 20 & 20 & 15 & 15 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle20.txt} & \input{../output/dmpc/angle20.txt} & \input{../output/dppc/angle15.txt} & \input{../output/dmpg/angle15.txt} \\
		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough20.txt} & \input{../output/dmpc/rough20.txt} & \input{../output/dppc/rough15.txt} & \input{../output/dmpg/rough15.txt} \\
    \hline
    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh20.txt} & \input{../output/dmpc/solh20.txt} & \input{../output/dppc/solh15.txt} & \input{../output/dmpg/solh15.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail20.txt} & \input{../output/dmpc/tail20.txt} & \input{../output/dppc/tail15.txt} & \input{../output/dmpg/tail15.txt} \\
	\end{tabular}
\end{table}
%

\section{Neutron reflectometry and SLD profiles}
Figure \ref{fig:neutron} shows the neutron reflectomery and scattering length density profiles for DMPC at \SI{25}{\milli\newton\per\meter} (two contrasts) and DPPC at \SI{15}{\milli\newton\per\meter} (two contrasts).
%
\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{figures/dmpc_25n_ref_sld}
	\includegraphics[width=0.9\textwidth]{figures/dppc_15n_ref_sld}
	\caption{The NR and SLD profiles at a surface pressure of (a) 25 mNm$^{-1}$ for two contrasts of DMPC, and (b) 15 mNm$^{-1}$ for two contrasts of DPPC. The NR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by \SI{5e-6}{\per\square\angstrom}, for clarity.}
	\label{fig:neutron}
\end{figure}
%

@@

	\includegraphics[width=0.50\textwidth]{figures/dmpc1_all_corner}

@@

@@

	\includegraphics[width=0.50\textwidth]{figures/dppc1_all_corner}

@@

@@

	\includegraphics[width=0.50\textwidth]{figures/dmpg1_all_corner}

@@
